Usage metrics

### 2020-12-17 analysis/usage.Rmd
More

```{r include=F}
E %>%
  filter(opcodes > 0) %>%
  filter(opcodes < 50) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Events per package", x = "") +
  theme(legend.position = "none")

>>>>

```{r include=F}
E %>%
  filter(opcodes > 0) %>% # == 0 if from eval.parent, because we do not count eval loops for it
  filter(opcodes <= 50) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Events per package", x = "") +
  theme(legend.position = "none")
